Adapting the Chumbley Score to match striae on Land Engraved Areas of bullets

### 2018-09-19 doc/paper.Rmd
commented out sentences
update to percentages

errorsCV <- rbind(errorsCV1, errorsCV2)
ggerrors <- errorsCV %>%
  ggplot(aes(x = wo, y = beta, colour=factor(alpha), linetype=factor(alpha))) +
  geom_point(aes(shape=factor(wv)), size=2.5) +
  geom_smooth(aes(group=alpha), se=FALSE, method="loess", span=1,  size=.7) +
  theme_bw() +
  scale_colour_brewer(expression("Nominal\ntype I error"~alpha),
                      palette="Set2", guide=FALSE) +
  scale_linetype_manual(values = c(2,1,3,4), guide=FALSE)+
  scale_shape_discrete(expression("Size of\nvalidation window "~w[v])) +
  guides(
    colour = guide_legend(override.aes = list(linetype= c(2,1,3,4)))
  )+
  xlab(expression("Window size for optimization "~w[o])) +
  ylab("Type II error rate") +
  facet_wrap(~method, labeller="label_both")

@@

cvcs %>% filter(!wo %in% c(130, 140)) %>%
  ggplot(aes(d = as.numeric(match), m = 1-p_value)) + 
  geom_roc(labels=FALSE, n.cuts=500, pointsize=0, size=0.6, 
           aes(colour = method.wo, linetype= method.wo)) + 
  facet_wrap(~wv, labeller = label_bquote(w[v] == .(wv))) +
    scale_linetype_manual(values=c(2,2,2,2,2,1,1,1,1,1), guide = FALSE) +
  scale_alpha_discrete(range=c(0.1, 0.6)) +
  scale_colour_manual(expression("Method /\nOptimization\nwindow size"~w[o]), values=cols) +
  theme_bw() +
  xlab("False Positives Rate (1 - Specificity)") +
  ylab("True Positives Rate (Sensitivity)") +
  guides(
   colour = guide_legend(override.aes = list(linetype = c(2,2,2,2,2,1,1,1,1,1)), ncol=2)
  ) +
  geom_abline(slope=-1, intercept = 1, linetype = 3, 
              colour="grey30", size = 0.25)

@@

p1 <- roc.summary %>% filter(!(wo %in% c(130, 140))) %>%
  ggplot(aes( x = wo, y=eer, colour=method, shape=method)) +
  geom_point(size=2) +
  facet_wrap(~wv, labeller = label_bquote(w[v] == .(wv))) + 
  theme_bw() +
  ylab("Equal Error rate (EER)") +
  xlab("Size of optimization window in pixels") +
  theme(legend.position = "bottom") + #c(0.25, 0.25)) +
  scale_colour_brewer("Method", palette="Set1") +
  scale_shape("Method") +
  scale_y_continuous(limits=c(0, 0.25))

@@

```{r type1, fig.width=7.75, fig.height=5.25, out.width='\\textwidth', fig.cap="Comparison of observed and nominal type I error rates  across a range of window sizes for optimization $wo$. The horizontal line in each facet indicates the nominal type I error rate."}
errorsCV$wv.method <- paste(errorsCV$method, errorsCV$wv, sep=" / ")
errorsCV %>% filter(wv %in% c(30,50)) %>%
  ggplot(aes(x = wo, y = actual, colour=factor(alpha), 
             linetype=method)) + 
  geom_hline(aes(yintercept=alpha), colour="grey30", size=.5) +
  geom_point(aes(shape=factor(wv.method)), size=2.5) +
  geom_smooth(aes(group=factor(method)), 
              size=.8, se=FALSE, method="lm", alpha=.9) +
  theme_bw() +
  ylab(expression("Observed type I error rate "~hat(alpha))) +
  xlab(expression("Window size for optimization "~w[o])) +
  scale_colour_brewer(
    expression("Nominal type I error "~alpha), palette="Set2") +
  facet_wrap(~alpha, labeller=label_bquote(alpha == .(alpha)), scales="free") +
  theme(legend.position="bottom") +
  scale_shape_manual(expression("Method / Validation window "~w[v]), values=c(1,2,16,17)) +
  scale_linetype_manual("Method", values=c(3,1), guide=FALSE) +
  guides(shape = guide_legend(ncol=2),
         col = guide_legend(ncol=2))

@@

h44.summ %>% gather(type, value, AUC, EER) %>% 
  filter(wv %in% c(75, 125), coarseness==0.125,
         between(wo, 210, 390)) %>% 
  ggplot(aes(x = wo, y = value, colour=Method, shape=factor(wv)))  +
  geom_point(size=2.5) +
#  geom_point(aes(y = lower), size=1) +
#  geom_point(aes(y = upper), size=1) +
  facet_wrap(~type, scales="free") +
  theme_bw() +
  scale_colour_brewer(palette="Set1", guide = guide_legend(ncol = 1)) +
  geom_smooth(aes(linetype = factor(wv), colour=Method), se=FALSE, span=2) +
  xlab(expression("Size of optimization window "~w[o]~" in pixels")) +
  ylab("Value") +
  theme(legend.position = "bottom", 
        legend.key.width = unit(2,"line")) +
  scale_shape(expression("Size of validation window "~w[v]~" in pixels"), guide = guide_legend(ncol=1))+
  scale_linetype(expression("Size of validation window "~w[v]~" in pixels"), guide = guide_legend(ncol=1))

>>>>

errorsCV <- rbind(errorsCV1, errorsCV2)
ggerrors <- errorsCV %>%
  ggplot(aes(x = wo, y = 100*beta, colour=factor(alpha*100), linetype=factor(100*alpha))) +
  geom_point(aes(shape=factor(wv)), size=2.5) +
  geom_smooth(aes(group=alpha), se=FALSE, method="loess", span=1,  size=.7) +
  theme_bw() +
  scale_colour_brewer(expression("Nominal Percent \nFalse Positives "~alpha),
                      palette="Set2", guide=FALSE) +
  scale_linetype_manual(values = c(2,1,3,4), guide=FALSE)+
  scale_shape_discrete(expression("Size of\nvalidation window "~w[v])) +
  guides(
    colour = guide_legend(override.aes = list(linetype= c(2,1,3,4)))
  )+
  xlab(expression("Window size for optimization "~w[o])) +
  ylab("Percent False Negatives") +
  facet_wrap(~method, labeller="label_both")

@@

cvcs %>% filter(!wo %in% c(130, 140)) %>%
  ggplot(aes(d = as.numeric(match), m = 1-p_value)) +
  geom_roc(labels=FALSE, n.cuts=500, pointsize=0, size=0.6, 
           aes(colour = method.wo, linetype= method.wo)) + 
  facet_wrap(~wv, labeller = label_bquote(w[v] == .(wv))) +
    scale_linetype_manual(values=c(2,2,2,2,2,1,1,1,1,1), guide = FALSE) +
  scale_alpha_discrete(range=c(0.1, 0.6)) +
  scale_colour_manual(expression("Method /\nOptimization\nwindow size"~w[o]), values=cols) +
  theme_bw() +
  xlab("Percent False Positives (100 - Specificity)") +
  ylab("Percent True Positives (Sensitivity)") +
  guides(
   colour = guide_legend(override.aes = list(linetype = c(2,2,2,2,2,1,1,1,1,1)), ncol=2)
  ) +
  geom_abline(slope=-1, intercept = 1, linetype = 3, 
              colour="grey30", size = 0.25) +
  scale_x_continuous(labels=c("0", "25", "50", "75", "100")) +
  scale_y_continuous(labels=c("0", "25", "50", "75", "100"))

@@

p1 <- roc.summary %>% filter(!(wo %in% c(130, 140))) %>%
  ggplot(aes( x = wo, y=eer*100, colour=method, shape=method)) +
  geom_point(size=2) +
  facet_wrap(~wv, labeller = label_bquote(w[v] == .(wv))) + 
  theme_bw() +
  ylab("Equal Error (EER) in Percent") +
  xlab("Size of optimization window in pixels") +
  theme(legend.position = "bottom") + #c(0.25, 0.25)) +
  scale_colour_brewer("Method", palette="Set1") +
  scale_shape("Method") +
  scale_y_continuous(limits=c(0, 0.25))

@@

```{r type1, fig.width=7.75, fig.height=5.25, out.width='\\textwidth', fig.cap="Comparison of observed and nominal type I error rates  across a range of window sizes for optimization $wo$. The horizontal line in each facet indicates the nominal type I error rate."}
errorsCV$wv.method <- paste(errorsCV$method, errorsCV$wv, sep=" / ")
errorsCV %>% filter(wv %in% c(30,50)) %>%
  ggplot(aes(x = wo, y = 100*actual, colour=factor(100*alpha), 
             linetype=method)) + 
  geom_hline(aes(yintercept=100*alpha), colour="grey30", size=.5) +
  geom_point(aes(shape=factor(wv.method)), size=2.5) +
  geom_smooth(aes(group=factor(method)), 
              size=.8, se=FALSE, method="lm", alpha=.9) +
  theme_bw() +
  ylab(expression("Observed Percent False Positives "~hat(alpha))) +
  xlab(expression("Window size for optimization "~w[o])) +
  scale_colour_brewer(
    expression("Nominal Percent False Positives "~alpha), palette="Set2") +
  facet_wrap(~alpha, labeller=label_bquote(alpha == .(alpha*100)), scales="free") +
  theme(legend.position="bottom") +
  scale_shape_manual(expression("Method / Validation window "~w[v]), values=c(1,2,16,17)) +
  scale_linetype_manual("Method", values=c(3,1), guide=FALSE) +
  guides(shape = guide_legend(ncol=2),
         col = guide_legend(ncol=2))

@@

h44.summ$EER <- 100*h44.summ$EER
h44.long <- h44.summ %>% gather(type, value, AUC, EER) %>% 
  filter(wv %in% c(75, 125), coarseness==0.125,
         between(wo, 210, 390)) 
h44.long$type <- factor(h44.long$type)

levels(h44.long$type)[2] <- "Percent Equal Error"

h44.long %>% 
  ggplot(aes(x = wo, y = value, colour=Method, shape=factor(wv)))  +
  geom_point(size=2.5) +
#  geom_point(aes(y = lower), size=1) +
#  geom_point(aes(y = upper), size=1) +
  facet_wrap(~type, scales="free") +
  theme_bw() +
  scale_colour_brewer(palette="Set1", guide = guide_legend(ncol = 1)) +
  geom_smooth(aes(linetype = factor(wv), colour=Method), se=FALSE, span=2) +
  xlab(expression("Size of optimization window "~w[o]~" in pixels")) +
  ylab("Value") +
  theme(legend.position = "bottom", 
        legend.key.width = unit(2,"line")) +
  scale_shape(expression("Size of validation window "~w[v]~" in pixels"), guide = guide_legend(ncol=1))+
  scale_linetype(expression("Size of validation window "~w[v]~" in pixels"), guide = guide_legend(ncol=1))
